# ndg params

A matching between the ndg parameter and the OS can be defined as

$$
\begin{cases}
m_s = \mu_\sigma - \frac{Z_P}{Z_S}\mu_\delta \\
m_c = \mu_\sigma + \frac{Z_P}{Z_S}\mu_\delta \\
\end{cases}
\quad\quad
\begin{cases}
\mu_\sigma =\frac{1}{2}(  m_s + m_c) \quad\,\,\,\,\\
\mu_\sigma =\frac{1}{2}\frac{Z_S}{Z_P}(  m_c - m_s) \\
\end{cases}
\,.
$$
This matching scheme has the problem that $\frac{Z_P}{Z_S}$ needs to be know very
precise to estimate well the cancellation in the $m_s$.

An alternative scheme used in the gm2 strange and charm paper is 
$$
\begin{cases}
m_c = \mu_\sigma + \frac{Z_P}{Z_S}\mu_\delta \\
aM_K^{ndg}(\mu_\sigma,\mu_\delta) = aM_K^{OS}(m_s)= aM_K^{OS}(m_s^{ref}) +(m_s^{ref}-m_s)\frac{\partial M_K^{OS}}{\partial m_s}\Bigg|_{m_s}  \\
\end{cases}
$$
where $m_s^{ref}$ is some value close enough to $m_s$ such higer order in the expansion
are negligible. The derivative is splitted in sea and valence contribution
$$
\frac{\partial M_K^{OS}}{\partial m_s}=\frac{\partial^{val} M_K^{OS}}{\partial m_s} +
\frac{\partial^{sea} M_K^{OS}}{\partial m_s}
$$
the derivative with respect to the valence is computed as finite difference and 
the derivative with respect to the sea is computed with the scalar insertions.

```{r}
df <- data.frame(
  "en" = c("B64", "C80","D54"),
  "kappa" = c(0.139426500000, 0.138752850000, 0.137972174000),
  "mul_sim" = c(0.00072, 0.0006, 0.00054),
  "musig_sim" = c(0.1315052, 0.107146000965, 0.087911000000),#0.077706999882
  "mudel_sim" = c(0.1246864, 0.106585999855, 0.086224000000),#0.074646999976
  "ms_sim" = c(0,0,0),
  "mc_sim" = c(0,0,0),
  "Zp_Zs" = c(0.79018,  0.82308, 0.85095),
  "mul" = c(0.0006669, 0.0005864, 0.0004934),
  "musig" = c(0,0,0),
  "mudel" = c(0,0,0),
  "ms" = c(0.018267,  0.016053, 0.013559),
  "mc" = c(0.23134,   0.19849, 0.16474)
)
```

```{r}
library(dplyr)
library(knitr)
# df$ms_sim<- df$musig_sim- df$
df <- mutate(df,
  ms_sim = musig_sim - Zp_Zs * mudel_sim,
  mc_sim = musig_sim + Zp_Zs * mudel_sim
)

df <- mutate(df,
  musig = (ms + mc) / 2,
  mudel = (mc - ms) / Zp_Zs / 2
)
print(df$mc_sim,digits = 12)
kable(df[, c(1:7)], digits = 20)
kable(df[, c(8:13)], digits = 20)
```


now we cange only the charm keeping the strange at the simulation point

```{r}
library(dplyr)
library(knitr)

df1 <- mutate(df,
  musig = (ms_sim + mc) / 2,
  mudel = (mc - ms_sim) / Zp_Zs / 2
)
  # musigma = 0.1260567
  # mudelta = 0.1332397
  # 2Kappamubar   = 0.0351512889651
  # 2KappaEpsBar  = 0.0371542900641
  # kappa = 0.1394265
  # 
  # #epsbar = 0.1394265
  # 2Kappamubar2  = 0.034769065158
  # 2KappaEpsBar2 = 0.036670563765
  # kappa2 = 0.1394265


kable(df1[, c(1, 2, 3, 4, 9, 10)], digits = 13)
```
```{r}
library(dplyr)
library(knitr)
# keeping ms fixed and change mc form
# mc_sim =0.2285992
mc_targ =0.22887328 # 0.1 of the iso-sim step
df1 <- mutate(df,
  musig = (ms_sim + mc_targ) / 2,
  mudel = (mc_targ - ms_sim) / Zp_Zs / 2
)
kable(df1[, c(1, 2, 3, 4,  10,11)], digits = 16)
options(digits=16)
cat("2*kap*mub = ", df1$kappa*2*df1$musig,"\n")
cat("2*kap*epsb = ", df1$kappa*2*df1$mudel,"\n")
cat("denominator\n")
cat("2*kap*mub = ", df1$kappa*2*df1$musig_sim,"\n")
cat("2*kap*epsb = ", df1$kappa*2*df1$mudel_sim,"\n")

```