# system scale setting


```{r ,include=FALSE}
library(Rose)
library(ggplot2)
library(plotly)
library(knitr)


df <- data.frame(x = 1:5, y = 1:5)
f1 <- function(df) {
  gg <- ggplot(df, aes(x, y)) +
    geom_point()
  assign("ggp", plotly::ggplotly(gg), envir = parent.frame())
  # ggp
  df # NOT returning a plot
}
res1 <- f1(df)
ggp # Let knit handle the plot
myplotly(ggplot())
masses <- c(
  0.0006669,
  0.018267,
  0.23134
)
```

```{r,results='asis',echo=FALSE, warning=FALSE}
cat("## FLAG\n")
df <- read.table("/home/garofalo/analysis/flow/data/fit_all_beta/data_from_fpi.txt", header = TRUE)
start_indices <- seq(2, ncol(df), by = 2)
new_df <- data.frame(df[, c(1, start_indices)])
colnames(new_df) <- colnames(df)[c(1, start_indices)]
new_df[, 1] <- df[, 1]
for (i in seq_along(start_indices)) {
  for (row in seq_along(df[, 1])) {
    new_df[row, i + 1] <- mean_print(df[row, start_indices[i]], df[row, start_indices[i] + 1])
  }
}
kable(new_df)

# kable(df)
cat("## wp25\n")
df <- read.table("/home/garofalo/analysis/flow/data/fit_all_beta/data_from_w0.txt", header = TRUE)
start_indices <- seq(2, ncol(df), by = 2)
new_df <- data.frame(df[, c(1, start_indices)])
colnames(new_df) <- colnames(df)[c(1, start_indices)]
new_df[, 1] <- df[, 1]
for (i in seq_along(start_indices)) {
  for (row in seq_along(df[, 1])) {
    new_df[row, i + 1] <- mean_print(df[row, start_indices[i]], df[row, start_indices[i] + 1])
  }
}
kable(new_df)

cat("## wp25_hybrid\n")
df <- read.table("/home/garofalo/analysis/flow/data/fit_all_beta/data_from_w0_hybrid.txt", header = TRUE)
start_indices <- seq(2, ncol(df), by = 2)
new_df <- data.frame(df[, c(1, start_indices)])
colnames(new_df) <- colnames(df)[c(1, start_indices)]
new_df[, 1] <- df[, 1]
for (i in seq_along(start_indices)) {
  for (row in seq_along(df[, 1])) {
    new_df[row, i + 1] <- mean_print(df[row, start_indices[i]], df[row, start_indices[i] + 1])
  }
}
kable(new_df)

cat("## wp25_deriv_mc_a2\n")
df <- read.table("/home/garofalo/analysis/flow/data/fit_all_beta/data_from_wp25_deriv_mc_a2.txt", header = TRUE)
df1 <- df
start_indices <- seq(2, ncol(df), by = 2)
new_df <- data.frame(df[, c(1, start_indices)])
colnames(new_df) <- colnames(df)[c(1, start_indices)]
new_df[, 1] <- df[, 1]
for (i in seq_along(start_indices)) {
  for (row in seq_along(df[, 1])) {
    new_df[row, i + 1] <- mean_print(df[row, start_indices[i]], df[row, start_indices[i] + 1])
  }
}
kable(new_df)


cat("## wp25_deriv_mc_a2_la_RDs\n")
df <- read.table("/home/garofalo/analysis/flow/data/fit_all_beta/data_from_wp25_deriv_mc_a2_la_RDs.txt", header = TRUE)
df_MD <- df
start_indices <- seq(2, ncol(df), by = 2)
new_df <- data.frame(df[, c(1, start_indices)])
colnames(new_df) <- colnames(df)[c(1, start_indices)]
new_df[, 1] <- df[, 1]
for (i in seq_along(start_indices)) {
  for (row in seq_along(df[, 1])) {
    new_df[row, i + 1] <- mean_print(df[row, start_indices[i]], df[row, start_indices[i] + 1])
  }
}
kable(new_df)

cat("## wp25_deriv_mc_a2_la_mc\n")
df <- read.table("/home/garofalo/analysis/flow/data/fit_all_beta/data_from_wp25_deriv_mc_a2_la_mc.txt", header = TRUE)
df_mc <- df
start_indices <- seq(2, ncol(df), by = 2)
new_df <- data.frame(df[, c(1, start_indices)])
colnames(new_df) <- colnames(df)[c(1, start_indices)]
new_df[, 1] <- df[, 1]
for (i in seq_along(start_indices)) {
  for (row in seq_along(df[, 1])) {
    new_df[row, i + 1] <- mean_print(df[row, start_indices[i]], df[row, start_indices[i] + 1])
  }
}
kable(new_df)
```

## difference in  mc 

We need to solve the system $T\vec{\delta\mu}=R^{sub}$ where $T_{ij}=\frac{\partial R_i}{\partial \mu_j}$ with
$R_i= M_i/f_\pi$ or $R_i=M_iw_0$ and $R^{sub}=R^{iso}-R^{sim}$.

Here we compare $\delta\mu_c$ when we add a term $C a^2$ to the physical value 
of $M_{D_s}$ adding to the system
$$
  T\vec{\delta\mu} = \vec{R^{sub}}+ a^2C \hat{e_{\mu_c}}
$$

The solution, writing the factor $a$ explicitelly is

$$
  a\vec{\delta\mu} = a T^{-1}(\vec{R^{sub}}+ a^2C \hat{e_{\mu_c}})
$$

With this modification $f_\pi$ becomes
$$
f_\pi= f_\pi^{sim}+ (a\vec{\delta \mu_c} +a^3C T^{-1}\hat{e_{\mu_c}})\frac{d f_\pi}{da\vec{\mu_c}}
$$

Alternatively to add the lattice artefact only on $\mu_c$ we can do
$$
  \frac{T}{a} a\vec{\delta\mu} = \vec{R^{sub}}+ a^3 C \frac{T}{a}\hat{e_{\mu_c}}
$$

$$
a\vec{\delta\mu} = a T^{-1}(\vec{R^{sub}}+ a^3C \frac{1}{a}T\hat{e_{\mu_c}})= 
aT^{-1}\vec{R^{sub}}+ a^3C\hat{e_{\mu_c}}
$$
(this can be done after adding the term $C$ to $\delta \mu$ after solving the sistem)
With this modification $f_\pi$ becomes
$$
f_\pi= f_\pi^{sim}+ (a\vec{\delta \mu} +a^3C\hat{e_{\mu_c}})\cdot\frac{d f_\pi}{da\vec{\mu}}
$$



```{r,results='asis',echo=FALSE, warning=FALSE}
gg <- myggplot(fill = FALSE)
gg <- ggplot() +
  theme_bw()
# diff<-(df1$delta_amuc - df_MD$delta_amuc)/df1$afpi
# gg <- gg + geom_point(aes(
#   x = df1$a.fm. * df1$a.fm.,
#   y = diff,
#   color="diff a2 MDs"
# ))
# gg <- gg + geom_errorbar(aes(
#   x = df1$a.fm. * df1$a.fm.,
#   y = diff,
#   ymin = diff- (df1$ddelta_amuc)/df1$afpi,
#   ymax = diff +(df1$ddelta_amuc)/df1$afpi,
#   color="diff a2 MDs"
# ), width=0.00005)
####
# diff_mc<-(df1$delta_amuc - df_mc$delta_amuc)/df1$afpi
# gg <- gg + geom_point(aes(
#   x = df1$a.fm. * df1$a.fm.,
#   y = diff_mc,
#   color="diff a2 mc"
# ))
# gg <- gg + geom_errorbar(aes(
#   x = df1$a.fm. * df1$a.fm.,
#   y = diff_mc,
#   ymin = diff_mc- (df1$ddelta_amuc)/df1$afpi,
#   ymax = diff_mc +(df1$ddelta_amuc)/df1$afpi,
#   color="diff a2 mc"
# ), width=0.00005)

######
gg <- gg + geom_point(aes(
  x = df1$a.fm. * df1$a.fm.,
  y = df1$delta_amuc / (df1$amul),
  color = "wp25"
))
# gg <- gg + geom_point(aes(
#   x = df1$a.fm. * df1$a.fm.,
#   y = df_mc$delta_amuc / (df1$amul),
#   color = "wp25+muc+a2*C"
# ))

for (ic in c(-1, -2,-3,-4, -5, -10)) {
  df_m <- read.table(paste0("/home/garofalo/analysis/flow/data/fit_all_beta/data_from_wp25_deriv_mc_a2_laC", ic, ".txt"), header = TRUE)
  gg <- gg + geom_point(aes(
    x = !!(df_m$a.fm. * df_m$a.fm.),
    y = !!(df_m$delta_amuc / (df1$amul)),
    color = !!paste0("MDs+a2*C=", ic)
  ))
}

# for (ic in c(-100, -200, -400, -800, -1600, -3200)) {
#   df_m <- read.table(paste0("/home/garofalo/analysis/flow/data/fit_all_beta/data_from_wp25_deriv_mc_a2_lamcC", ic, ".txt"), header = TRUE)
#   gg <- gg + geom_point(aes(
#     x = !!(df_m$a.fm. * df_m$a.fm.),
#     y = !!(df_m$delta_amuc / (df1$a.fm./197.3)),
#     color = !!paste0("mc+a2*C=", ic)
#   ))
# }
df_m <- read.table(paste0("/home/garofalo/analysis/flow/data/fit_all_beta/data_from_fpi.txt"), header = TRUE)
gg <- gg + geom_point(aes(
 x = !!(df_m$a.fm. * df_m$a.fm.),
   y = !!(df_m$delta_amuc / (df_m$a.fm./197.3)),
   color = "from fpi"
 ))

fig <- myplotly(gg, "", "$a^2$", "$\\delta\\mu_c /\\mu_\\ell$",
  xrange = c(0, 0.008),
  #yrange = c(-0.0002, 0.0006),
  to_print = TRUE
)
```



## w0


```{r,results='asis',echo=FALSE, warning=FALSE}
gg <- NULL
basenames <- c(
  #"/home/garofalo/analysis/flow/data/fit_all_beta/fit_w0_cont_a2",
  "/home/garofalo/analysis/flow/data/fit_all_beta_sim/fit_w0_cont_a2",
  #"/home/garofalo/analysis/flow/data/fit_all_beta_no_m0//fit_w0_cont_a2",
  #"/home/garofalo/analysis/flow/data/fit_all_beta/fit_w0_ens_cont_a2",
  #"/home/garofalo/analysis/flow/data/fit_all_beta/fit_w0_hybrid_cont_a2",
  "/home/garofalo/analysis/flow/data/fit_all_beta/fit_w0_lin_deriv_cont_a2",
  "/home/garofalo/analysis/flow/data/fit_all_beta/fit_w0_fpi_wp25_Cm5_cont_a2"
  # "/home/garofalo/analysis/flow/data/fit_all_beta_nocharmw0//fit_w0_cont_a2",
  # "/home/garofalo/analysis/flow/data/fit_all_beta_nocharmw0_decorr///fit_w0_cont_a2"
)
labels <- c(
  #"P[0]+ P[1]*a2 ",
  "sim-point",
  #"no m0 corr",
  #"sea-deriv-ens",
  #"hybrid",
  "lin_deriv",
  "fpi-from-wp25+C-5"
  # "no-charm-corr-w0",
  # "no-charm-corr-w0-decorr"
)


for (j in seq_along(basenames)) {
  print(basenames[j])
  fit <- Rose::read_fit_P_file(paste0(basenames[j], "_fit_P.dat"))
  make_table_fit_result(fit)
  gg <- plot_fit(basenames[j], "a2",
    # noline = TRUE,
    data_type = c(labels[j]),
    gg = gg,
    id_x = 1,
    single_name_for_fit = labels[j],
    width = 0.0001
  )
}
w0_wp25 <- 0.17236
gg <- gg + geom_hline(yintercept = w0_wp25, linetype = "dashed")
gg <- gg + geom_point(aes(x = 0, y = w0_wp25, color = "wp25", shape = "wp25", fill = "wp25"))

fig <- myplotly(gg, "", "$a^2 [\\mbox{fm}^2]$", "$w_0 [\\mbox{fm}]$",
  to_print = TRUE,
  # yrange = c(-1, 4),
  legend_position = c(0.7, 0.98)
)
```




## sqrtt0


```{r,results='asis',echo=FALSE, warning=FALSE}
gg <- NULL
basenames <- c(
  "/home/garofalo/analysis/flow/data/fit_all_beta/fit_sqrtt0_from_fpi_cont_a2",
  "/home/garofalo/analysis/flow/data/fit_all_beta/fit_sqrtt0_wp25_C0.000000_cont_a2",
  "/home/garofalo/analysis/flow/data/fit_all_beta/fit_sqrtt0_wp25_C-5.000000_cont_a2"
)
labels <- c(
  "FLAG ",
  "wp25",
  "wp25+C-5"
)


for (j in seq_along(basenames)) {
  print(basenames[j])
  fit <- Rose::read_fit_P_file(paste0(basenames[j], "_fit_P.dat"))
  print(make_table_fit_result(fit))
  gg <- plot_fit(basenames[j], "a2",
    # noline = TRUE,
    data_type = c(labels[j]),
    gg = gg,
    id_x = 1,
    single_name_for_fit = labels[j],
    width = 0.0001
  )
}
w0_wp25 <- 0.14292
gg <- gg + geom_hline(yintercept = w0_wp25, linetype = "dashed")
gg <- gg + geom_point(aes(x = 0, y = w0_wp25, color = "FLAG24", shape = "FLAG24", fill = "FLAG24"))

fig <- myplotly(gg, "", "$a^2 [\\mbox{fm}^2]$", "$\\sqrt{t_0} [\\mbox{fm}]$",
  to_print = TRUE,
  # yrange = c(-1, 4),
  legend_position = c(0, 0.98)
)
```

## fpi

```{r,results='asis',echo=FALSE, warning=FALSE}
gg <- NULL
basenames <- c(
  "/home/garofalo/analysis/flow/data/fit_all_beta/fit_fpi_cont_a2",
  "/home/garofalo/analysis/flow/data/fit_all_beta/fit_fpi_hybrid_cont_a2",
  "/home/garofalo/analysis/flow/data/fit_all_beta/fit_fpi_Mpi_wp25_hybrid_cont_a2",
  "/home/garofalo/analysis/flow/data/fit_all_beta/fit_fpi_wp25_lin_cont_a2",
  "/home/garofalo/analysis/flow/data/fit_all_beta/fit_fpi_wp25_lin_laRDs_cont_a2",
  "/home/garofalo/analysis/flow/data/fit_all_beta/fit_fpi_wp25_lin_laRDs_exact_cont_a2",
  "/home/garofalo/analysis/flow/data/fit_all_beta/fit_fpi_wp25_lin_la_mc_exact_cont_a2"
)
labels <- c(
  "P[0]+ P[1]*a2 ",
  "w0 hybrid",
  "wp25Mpi_hybrid",
  "wp25_lin_dmc",
  "wp25_lin_dmc_laRDs",
  "wp25_lin_dmc_laRDs_exact",
  "wp25_lin_dmc_la_mc_exact"
)


for (j in seq_along(basenames)) {
  print(basenames[j])
  fit <- Rose::read_fit_P_file(paste0(basenames[j], "_fit_P.dat"))
  print(make_table_fit_result(fit))
  gg <- plot_fit(basenames[j], "a2",
    # noline = TRUE,
    data_type = labels[j],
    gg = gg,
    id_x = 1,
    single_name_for_fit = labels[j],
    width = 0.0001,
    nudge = j * 0.00001
  )
}
fpi_FLAG <- 130.5
gg <- gg + geom_hline(yintercept = fpi_FLAG, linetype = "dashed") #+annotate("text", x = 0.0002, y = fpi_FLAG-0.2, label="FLAG")
gg <- gg + geom_point(aes(x = 0, y = fpi_FLAG, color = "FLAG", shape = "FLAG", fill = "FLAG"))

fig <- myplotly(gg, "", "$a^2 [\\mbox{fm}^2]$", "$f_{\\pi} [\\mbox{MeV}]$",
  to_print = TRUE,
  # yrange = c(-1, 4),
  legend_position = c(0.7, 0.98)
)
```

## AIC fpi

```{r,results='asis',echo=FALSE, warning=FALSE}
gg <- NULL
dir <- "/home/garofalo/analysis/flow/data/fit_all_beta/"
basenames <- c(
  "fit_fpi_wp25_lin_a2",
  "fit_fpi_wp25_lin_a2_3pt",
  "fit_fpi_wp25_lin_a2_a4",
  "fit_fpi_wp25_lin_a2_3pt_noC"
)
# labels <- c(  "a2",  "a2_3pt",  "a2_a4")
count <- length(basenames)
df <- data.frame(
  "fit" = rep("", count),
  "res" = rep(0, count),
  "err" = rep(0, count),
  "chi2dof" = rep(0, count),
  "dof" = rep(0, count),
  "Npar" = rep(0, count),
  "Ndat" = rep(0, count),
  "mult" = rep(0, count),
  "k" = rep(0, count)
)

for (j in seq_along(basenames)) {
  print(basenames[j])
  fit <- Rose::read_fit_P_file(paste0(dir, basenames[j], "_fit_P.dat"))
  df[j, 1] <- basenames[j]
  M <- data.matrix(fit$C)
  for (i in c(1:dim(M)[1])) {
    for (l in c(1:dim(M)[1])) {
      M[i, l] <- as.numeric(fit$C[i, l])
    }
  }
  e <- eigen(M)

  lmin <- min(abs(e$values))
  lmax <- max(abs(e$values))
  k <- lmax / lmin
  df[j, -1] <- c(fit$P[1, 2], fit$P[1, 3], fit$chi2dof, fit$dof, fit$npar, fit$ndata, 1, k)


  # print(make_table_fit_result(fit))
  gg <- plot_fit(paste0(dir, basenames[j]), "a2",
    # noline = TRUE,
    data_type = basenames[j],
    gg = gg,
    id_x = 1,
    single_name_for_fit = basenames[j],
    width = 0.0001,
    nudge = j * 0.00001
  )
}
fpi_FLAG <- 130.5
gg <- gg + geom_hline(yintercept = fpi_FLAG, linetype = "dashed") #+annotate("text", x = 0.0002, y = fpi_FLAG-0.2, label="FLAG")
gg <- gg + geom_point(aes(x = 0, y = fpi_FLAG, color = "FLAG", shape = "FLAG", fill = "FLAG"))

#### AIC
ave_BAIC <- BAIC(v = df$res, err = df$err, chi2dof = df$chi2dof, dof = df$dof, npar = df$Npar, multiplicity = df$mult)
tab <- data.frame("fit" = basenames, "$f_{\\pi} [\\mbox{MeV}]$" = mapply(mean_print, df$res, df$err), "BAIC" = ave_BAIC$AIC, "chi2dof" = df$chi2dof, "lmax/lmin" = df$k)
kable(tab, col.names = c("fit", "$f_{\\pi}[\\text{MeV}]$", "BAIC", "$\\chi^2/dof$", "$\\lambda_{max}/\\lambda_{min}$"))
cat("BAIC average $f_\\pi=", mean_print(ave_BAIC$m, ave_BAIC$dm), "\\,[\\text{MeV}]$<br>")
#### remove a4
dff <- df[!grepl("a4", df$fit), ]
ave_BAICf <- BAIC(v = dff$res, err = dff$err, chi2dof = dff$chi2dof, dof = dff$dof, npar = dff$Npar, multiplicity = dff$mult)
cat("BAIC average no a4 $f_\\pi=", mean_print(ave_BAICf$m, ave_BAICf$dm), "\\,[\\text{MeV}]$<br>")
####
dff <- df[c(1, 2), ]
ave_BAICf <- BAIC(v = dff$res, err = dff$err, chi2dof = dff$chi2dof, dof = dff$dof, npar = dff$Npar, multiplicity = dff$mult)
cat("BAIC 1,2 $f_\\pi=", mean_print(ave_BAICf$m, ave_BAICf$dm), "\\,[\\text{MeV}]$<br>")




fig <- myplotly(gg, "", "$a^2 [\\mbox{fm}^2]$", "$f_{\\pi} [\\mbox{MeV}]$",
  to_print = TRUE,
  # yrange = c(-1, 4),
  legend_position = c(0.7, 0.98)
)
```


## fpi + C a^2 MDs

```{r,results='asis',echo=FALSE, warning=FALSE}
gg <- NULL
library(stringr)
basenames <- c(
  "/home/garofalo/analysis/flow/data/fit_all_beta/fit_fpi_wp25_lin_cont_a2",
  "/home/garofalo/analysis/flow/data/fit_all_beta/fit_fpi_wp25_C-1.000000_cont_a2",
  "/home/garofalo/analysis/flow/data/fit_all_beta/fit_fpi_wp25_C-2.000000_cont_a2",
  "/home/garofalo/analysis/flow/data/fit_all_beta/fit_fpi_wp25_C-3.000000_cont_a2",
  "/home/garofalo/analysis/flow/data/fit_all_beta/fit_fpi_wp25_C-4.000000_cont_a2",
  "/home/garofalo/analysis/flow/data/fit_all_beta/fit_fpi_wp25_C-5.000000_cont_a2",
  "/home/garofalo/analysis/flow/data/fit_all_beta/fit_fpi_wp25_C-6.000000_cont_a2",
  "/home/garofalo/analysis/flow/data/fit_all_beta/fit_fpi_wp25_C-7.000000_cont_a2",
  "/home/garofalo/analysis/flow/data/fit_all_beta/fit_fpi_wp25_C-10.000000_cont_a2"
)
# extract the C value from the string
c_value <- as.numeric(sub(".*_C([^_]+)_.*", "\\1", basenames))
c_value[is.na(c_value)] <- 0
labels <- paste0("C=", c_value)


for (j in seq_along(basenames)) {
  print(basenames[j])
  fit <- Rose::read_fit_P_file(paste0(basenames[j], "_fit_P.dat"))
  print(make_table_fit_result(fit))
  gg <- plot_fit(basenames[j], "a2",
    # noline = TRUE,
    data_type = labels[j],
    gg = gg,
    id_x = 1,
    single_name_for_fit = labels[j],
    width = 0.0001,
    nudge = j * 0.00001,
    noribbon = FALSE,
    noline = TRUE
  )
}
fpi_FLAG <- 130.5
gg <- gg + geom_hline(yintercept = fpi_FLAG, linetype = "dashed") #+annotate("text", x = 0.0002, y = fpi_FLAG-0.2, label="FLAG")
gg <- gg + geom_point(aes(x = 0, y = fpi_FLAG, color = "FLAG", shape = "FLAG", fill = "FLAG"))

fig <- myplotly(gg, "", "$a^2 [\\mbox{fm}^2]$", "$f_{\\pi} [\\mbox{MeV}]$",
  to_print = TRUE,
  # yrange = c(-1, 4),
  legend_position = c(0.7, 0.98)
)
```


## fpi + C a^2 mc

```{r,results='asis',echo=FALSE, warning=FALSE}
gg <- NULL
library(stringr)
basenames <- c(
  "/home/garofalo/analysis/flow/data/fit_all_beta/fit_fpi_wp25_lin_cont_a2",
  "/home/garofalo/analysis/flow/data/fit_all_beta/fit_fpi_wp25_mc_C-100.000000_cont_a2",
  "/home/garofalo/analysis/flow/data/fit_all_beta/fit_fpi_wp25_mc_C-200.000000_cont_a2",
  "/home/garofalo/analysis/flow/data/fit_all_beta/fit_fpi_wp25_mc_C-400.000000_cont_a2",
  "/home/garofalo/analysis/flow/data/fit_all_beta/fit_fpi_wp25_mc_C-800.000000_cont_a2",
  "/home/garofalo/analysis/flow/data/fit_all_beta/fit_fpi_wp25_mc_C-1600.000000_cont_a2",
  "/home/garofalo/analysis/flow/data/fit_all_beta/fit_fpi_wp25_mc_C-3200.000000_cont_a2"
)
# extract the C value from the string
c_value <- as.numeric(sub(".*mc_C([^_]+)_.*", "\\1", basenames))
c_value[is.na(c_value)] <- 0
labels <- paste0("C=", c_value)


for (j in seq_along(basenames)) {
  print(basenames[j])
  fit <- Rose::read_fit_P_file(paste0(basenames[j], "_fit_P.dat"))
  print(make_table_fit_result(fit))
  gg <- plot_fit(basenames[j], "a2",
    # noline = TRUE,
    data_type = labels[j],
    gg = gg,
    id_x = 1,
    single_name_for_fit = labels[j],
    width = 0.0001,
    nudge = j * 0.00001
  )
}
fpi_FLAG <- 130.5
gg <- gg + geom_hline(yintercept = fpi_FLAG, linetype = "dashed") #+annotate("text", x = 0.0002, y = fpi_FLAG-0.2, label="FLAG")
gg <- gg + geom_point(aes(x = 0, y = fpi_FLAG, color = "FLAG", shape = "FLAG", fill = "FLAG"))

fig <- myplotly(gg, "", "$a^2 [\\mbox{fm}^2]$", "$f_{\\pi} [\\mbox{MeV}]$",
  to_print = TRUE,
  # yrange = c(-1, 4),
  legend_position = c(0.7, 0.98)
)
```

## fpi 3 reg

```{r,results='asis',echo=FALSE, warning=FALSE}
library(stringr)
dft <- NULL
for (C in c(0, -3, -4, -5, -6, -7)) {
  gg <- NULL
  path <- "/home/garofalo/analysis/flow/data/fit_all_beta/"
  basenames <- c(
    paste0("fit_fpi_C", C, ".000000_N3_a2"),
    paste0("fit_fpi_C", C, ".000000_N3_a2_noBOS_noBtm_noBWTI"),
    # paste0("fit_fpi_C", C, ".000000_N3_a2_a4"),
    # paste0("fit_fpi_C", C, ".000000_N3_a2_Husung0.42"),
    # paste0("fit_fpi_C", C, ".000000_N3_a2_Husung0.21"),
    paste0("fit_fpi_C", C, ".000000_N3_a2_noCOS_noCtm_noCWTI"),
    paste0("fit_fpi_C", C, ".000000_N3_a2_a4WTI"),
    paste0("fit_fpi_C", C, ".000000_N3_a2_a4tm"),
    paste0("fit_fpi_C", C, ".000000_N3_a2_a4OS"),
    paste0("fit_fpi_C", C, ".000000_N3_a2_a4_noa4WTI"),
    paste0("fit_fpi_C", C, ".000000_N3_a2_a4_noa4tm"),
    paste0("fit_fpi_C", C, ".000000_N3_a2_a4_noa4OS"),
    paste0("fit_fpi_C", C, ".000000_N3_a2_HusungWTI"),
    paste0("fit_fpi_C", C, ".000000_N3_a2_Husungtm"),
    paste0("fit_fpi_C", C, ".000000_N3_a2_HusungOS")
    )
  legend_name <- gsub("fit_fpi_|\\.000000", "", basenames)
  count <- length(basenames)
  df <- data.frame(
    "fit" = rep("", count),
    "res" = rep(0, count),
    "err" = rep(0, count),
    "chi2dof" = rep(0, count),
    "dof" = rep(0, count),
    "Npar" = rep(0, count),
    "Ndat" = rep(0, count),
    "mult" = rep(0, count),
    "k" = rep(0, count)
  )

  # extract the C value from the string
  labels <- list(c("WTI", "tm", "OS"))

  for (j in seq_along(basenames)) {
    # print(basenames[j])
    fit <- Rose::read_fit_P_file(paste0(path, basenames[j], "_fit_P.dat"))
    # print(make_table_fit_result(fit))
    df[j, 1] <- basenames[j]
    # M <- data.matrix(fit$C)
    # for (i in c(1:dim(M)[1])) {
    #   for (l in c(1:dim(M)[1])) {
    #     M[i, l] <- as.numeric(fit$C[i, l])
    #   }
    # }
    M <- matrix(as.numeric(as.matrix(fit$C)), nrow = nrow(fit$C))
    e <- eigen(M)

    lmin <- min(abs(e$values))
    lmax <- max(abs(e$values))
    k <- lmax / lmin
    df[j, -1] <- c(fit$P[1, 2], fit$P[1, 3], fit$chi2dof, fit$dof, fit$npar, fit$ndata, 1, k)

    gg <- plot_fit(paste0(path, basenames[j]), "a2",
      # noline = TRUE,
      data_type = labels[[1]],
      gg = gg,
      id_x = 1,
      single_name_for_fit = legend_name[j],
      # labelfit = "fit",
      width = 0.0001,
      nudge = 0,
      noline = TRUE
    )
  }
  cat("C=", C, "<br>\n")
  fpi_FLAG <- 130.5
  gg <- gg + geom_hline(yintercept = fpi_FLAG, linetype = "dashed") #+annotate("text", x = 0.0002, y = fpi_FLAG-0.2, label="FLAG")
  gg <- gg + geom_point(aes(x = 0, y = fpi_FLAG, color = "FLAG", shape = "FLAG", fill = "FLAG"))
  #### BAIC
  ave_BAIC <- BAIC(v = df$res, err = df$err, chi2dof = df$chi2dof, dof = df$dof, npar = df$Npar, multiplicity = df$mult)
  tab <- data.frame("fit" = basenames, "$f_{\\pi} [\\mbox{MeV}]$" = mapply(mean_print, df$res, df$err), "BAIC" = ave_BAIC$AIC, "chi2dof" = df$chi2dof, "lmax/lmin" = df$k)
  print(kable(tab, col.names = c("fit", "$f_{\\pi}[\\text{MeV}]$", "BAIC", "$\\chi^2/dof$", "$\\lambda_{max}/\\lambda_{min}$")))
  cat("BAIC average $f_\\pi=", ave_BAIC$m, "(", ave_BAIC$stat, ")(", ave_BAIC$syst, ") =", mean_print(ave_BAIC$m, ave_BAIC$dm), "\\,[\\text{MeV}]$<br>\n")

  ## only linear fit
  # df1 <- df[c(1, 2, 6), ]
  # ave_BAIC1 <- BAIC(v = df1$res, err = df1$err, chi2dof = df1$chi2dof, dof = df1$dof, npar = df1$Npar, multiplicity = df1$mult)
  # cat("BAIC average (1,2,6) $f_\\pi=", ave_BAIC1$m, "(", ave_BAIC1$stat, ")(", ave_BAIC1$syst, ") =", mean_print(ave_BAIC1$m, ave_BAIC1$dm), "\\,[\\text{MeV}]$<br>\n")
  ## only linear fit
  # df1 <- df[c(-3, -4, -5), ]
  # ave_BAIC1 <- BAIC(v = df1$res, err = df1$err, chi2dof = df1$chi2dof, dof = df1$dof, npar = df1$Npar, multiplicity = df1$mult)
  # cat("BAIC average linear c(-3,-4,-5)  $f_\\pi=", ave_BAIC1$m, "(", ave_BAIC1$stat, ")(", ave_BAIC1$syst, ") =", mean_print(ave_BAIC1$m, ave_BAIC1$dm), "\\,[\\text{MeV}]$<br>\n")

  ###
  dft <- rbind(dft, df)

  fig <- myplotly(gg, "", "$a^2 [\\mbox{fm}^2]$", "$f_{\\pi} [\\mbox{MeV}]$",
    to_print = TRUE,
    # yrange = c(-1, 4),
    legend_position = c(0.7, 0.98)
  )
}
cat("<br>BAIC average all\n\n")
df1 <- dft
ave_BAIC1 <- BAIC(v = df1$res, err = df1$err, chi2dof = df1$chi2dof, dof = df1$dof, npar = df1$Npar, multiplicity = df1$mult)
cat("BAIC $f_\\pi=", mean_print(ave_BAIC1$m, ave_BAIC1$dm), "\\,[\\text{MeV}]$<br>")
df1 <- dft[!grepl("a4$", dft$fit) & !grepl("Husung", dft$fit), ]
ave_BAIC1 <- BAIC(v = df1$res, err = df1$err, chi2dof = df1$chi2dof, dof = df1$dof, npar = df1$Npar, multiplicity = df1$mult)
cat("BAIC (no a4 all) (no log)  $f_\\pi=", mean_print(ave_BAIC1$m, ave_BAIC1$dm), "\\,[\\text{MeV}]$<br>\n")
df1 <- dft[!grepl("a4$", dft$fit) & !grepl("Husung", dft$fit) & !grepl("C0.0", dft$fit), ]
ave_BAIC1 <- BAIC(v = df1$res, err = df1$err, chi2dof = df1$chi2dof, dof = df1$dof, npar = df1$Npar, multiplicity = df1$mult)
cat("BAIC (no C0) (no a4 all) (no log)  $f_\\pi=", mean_print(ave_BAIC1$m, ave_BAIC1$dm), "\\,[\\text{MeV}]$<br>\n")
```


## MDs

```{r,results='asis',echo=FALSE, warning=FALSE}
gg <- NULL
basenames <- c(
  "/home/garofalo/analysis/flow/data/fit_all_beta/fit_MDs_wp25_lin_laRDs_exact_cont_a2",
  "/home/garofalo/analysis/flow/data/fit_all_beta/fit_MDs_wp25_lin_la_mc_exact_cont_a2"
)
labels <- c(
  "wp25_lin_dmc_laRDs_exact",
  "wp25_lin_dmc_la_mc_exact"
)


for (j in seq_along(basenames)) {
  print(basenames[j])
  fit <- Rose::read_fit_P_file(paste0(basenames[j], "_fit_P.dat"))
  print(make_table_fit_result(fit))
  gg <- plot_fit(basenames[j], "a2",
    # noline = TRUE,
    data_type = labels[j],
    gg = gg,
    id_x = 1,
    single_name_for_fit = labels[j],
    width = 0.0001,
    nudge = j * 0.0000001
  )
}
MDs_FLAG <- 1967
gg <- gg + geom_hline(yintercept = MDs_FLAG, linetype = "dashed") #+annotate("text", x = 0.0002, y = fpi_FLAG-0.2, label="FLAG")
gg <- gg + geom_point(aes(x = 0, y = MDs_FLAG, color = "FLAG", shape = "FLAG", fill = "FLAG"))

fig <- myplotly(gg, "", "$a^2 [\\mbox{fm}^2]$", "$M_{D_s} [\\mbox{MeV}]$",
  to_print = TRUE,
  # yrange = c(-1, 4),
  legend_position = c(0.7, 0.98)
)
```

## ms/ml



```{r,results='asis',echo=FALSE, warning=FALSE}
gg <- NULL
basenames <- c(
  "/home/garofalo/analysis/flow/data/fit_all_beta/fit_ms_over_ml_from_fpi_cont_a2",
  "/home/garofalo/analysis/flow/data/fit_all_beta/fit_ms_over_ml_from_w0_cont_a2",
  "/home/garofalo/analysis/flow/data/fit_all_beta/fit_ms_over_ml_from_w0_hybrid_cont_a2"
)
labels <- c(
  "FLAG",
  "wp25",
  "wp25_hybrid"
)


for (j in seq_along(basenames)) {
  print(basenames[j])
  fit <- Rose::read_fit_P_file(paste0(basenames[j], "_fit_P.dat"))
  make_table_fit_result(fit)
  gg <- plot_fit(basenames[j], "a2",
    # noline = TRUE,
    data_type = c(labels[j]),
    gg = gg,
    id_x = 1,
    single_name_for_fit = labels[j],
    width = 0.0001
  )
}

# Creazione del dataframe con valore centrale ed errore
df <- data.frame(
  x = 0,
  y = 27.227,
  incertezza = 0.081,
  lab = "FLAG24"
)

gg <- gg + geom_point(data = df, aes(x = x, y = y, color = lab, shape = lab, fill = lab)) +
  # Barra di errore (y +/- incertezza)
  geom_errorbar(
    data = df, aes(
      x = x,
      y = y,
      ymin = y - incertezza,
      ymax = y + incertezza, color = lab, shape = lab, fill = lab
    ),
    width = 0.0001
  )

fig <- myplotly(gg, "", "$a^2 [\\mbox{fm}^2]$", "$m_s/m_\\ell$",
  to_print = TRUE,
  # yrange = c(-1, 4),
  legend_position = c(0.7, 0.98)
)
```


```{r,results='asis',echo=FALSE, warning=FALSE}
gg <- NULL
basenames <- c(
  "/home/garofalo/analysis/flow/data/fit_all_beta/fit_mc_over_ms_from_fpi_cont_a2",
  "/home/garofalo/analysis/flow/data/fit_all_beta/fit_mc_over_ms_from_w0_cont_a2",
  "/home/garofalo/analysis/flow/data/fit_all_beta//fit_mc_over_ms_from_w0_hybrid_cont_a2"
)
labels <- c(
  "FLAG",
  "wp25",
  "wp25_hybrid"
)


for (j in seq_along(basenames)) {
  print(basenames[j])
  fit <- Rose::read_fit_P_file(paste0(basenames[j], "_fit_P.dat"))
  make_table_fit_result(fit)
  gg <- plot_fit(basenames[j], "a2",
    # noline = TRUE,
    data_type = c(labels[j]),
    gg = gg,
    id_x = 1,
    single_name_for_fit = labels[j],
    width = 0.0001
  )
}
# Creazione del dataframe con valore centrale ed errore
df <- data.frame(
  x = 0,
  y = 11.766,
  incertezza = 0.030,
  lab = "FLAG24"
)

gg <- gg + geom_point(data = df, aes(x = x, y = y, color = lab, shape = lab, fill = lab)) +
  # Barra di errore (y +/- incertezza)
  geom_errorbar(
    data = df, aes(
      x = x,
      y = y,
      ymin = y - incertezza,
      ymax = y + incertezza, color = lab, shape = lab, fill = lab
    ),
    width = 0.0001
  )

fig <- myplotly(gg, "", "$a^2 [\\mbox{fm}^2]$", "$m_c/m_s$",
  to_print = TRUE,
  # yrange = c(-1, 4),
  legend_position = c(0.7, 0.98)
)
```


```{r,results='asis',echo=FALSE, warning=FALSE}
gg <- NULL
basenames <- c(
  "/home/garofalo/analysis/flow/data/fit_all_beta/fit_a_ratio_FLAG_wp25_cont_a2",
  "/home/garofalo/analysis/flow/data/fit_all_beta/fit_a_ratio_FLAG_wp25hybrid_cont_a2"
)
labels <- c(
  "FLAG-wp25",
  "FLAG-wp25_hybr"
)

for (j in seq_along(basenames)) {
  print(basenames[j])
  fit <- Rose::read_fit_P_file(paste0(basenames[j], "_fit_P.dat"))
  make_table_fit_result(fit)
  gg <- plot_fit(basenames[j], "a2",
    # noline = TRUE,
    data_type = c(labels[j]),
    gg = gg,
    id_x = 1,
    single_name_for_fit = labels[j],
    width = 0.0001
  )
}

fig <- myplotly(gg, "", "$a^2_{FLAG} [\\mbox{fm}^2]$", "$a_{FLAG}/a_{wp25}$",
  to_print = TRUE,
  # yrange = c(-1, 4),
  legend_position = c(0.7, 0.98)
)
```


```{r,results='asis',echo=FALSE, warning=FALSE}
gg <- NULL
basenames <- c(
  "/home/garofalo/analysis/flow/data/fit_all_beta/fit_a_diff_FLAG_wp25_cont_a2",
  "/home/garofalo/analysis/flow/data/fit_all_beta/fit_a_diff_FLAG_wp25hybrid_cont_a2",
  "/home/garofalo/analysis/flow/data/fit_all_beta/fit_a_diff_FLAG_wp25Mpihybrid_cont_a2"
)
labels <- c(
  "FLAG-wp25",
  "FLAG-wp25_hybr",
  "FLAG-wp25Mpi_hybr"
)


for (j in seq_along(basenames)) {
  print(basenames[j])
  fit <- Rose::read_fit_P_file(paste0(basenames[j], "_fit_P.dat"))
  make_table_fit_result(fit)
  gg <- plot_fit(basenames[j], "a2",
    # noline = TRUE,
    data_type = c(labels[j]),
    gg = gg,
    id_x = 1,
    single_name_for_fit = labels[j],
    width = 0.0001
  )
}

fig <- myplotly(gg, "", "$a^2_{FLAG} [\\mbox{fm}^2]$", "$a_{FLAG}-a_{wp25}$",
  to_print = TRUE,
  # yrange = c(-1, 4),
  legend_position = c(0.7, 0.98)
)
```
